---
title: "Euro 2016 DIDE scores"
author: "Stephane"
date: "8 June 2016"
output: html_document
---

```{r}
library(knitr)
read_chunk('test.R')
```

```{r libs, warning=FALSE, message=FALSE}
```

Scoring system
```{r scoring system}

```

Load the google sheet
```{r read sheet}
```

Extract the predictions
```{r extract predictions}
```

Simulate real scores
```{r simulate real score}
```

Scoring function
```{r scoring function}
```

Results without bonus
```{r results without bonus}
```

Bonus
```{r bonus}
```


Final results
```{r final results}
```

```{r, results='asis'}
knitr::kable(rs1)
```

### Grand total
```{r grand total}
```


### Examples
```{r, echo = FALSE}
ex0 <- which(rs0 == 0, arr.ind = T) # zero
ex1 <- which(rs0 > 0 & bonusMatrix == 0, arr.ind = T) # no bonus
ex2 <- which(rs0 > 0 & bonusMatrix > 0, arr.ind = T) # bonus
exs <- list(ex0, ex1, ex2)
rc <- list()
for (k in 1:length(exs)){
  rc[[k]] <- exs[[k]][sample(nrow(exs[[k]]), 1),]
}
```
* For the game `r row.names(rs1)[rc[[1]][1]]`, with a real score of `r paste(real[rc[[1]][1],], collapse = " - ")`, `r colnames(rs1)[rc[[1]][2]]` predicted `r paste(preds[[rc[[1]][2]]][rc[[1]][1],], collapse = " - ")` and won `r rs0[rc[[1]][1], rc[[1]][2]]` points and `r bonusMatrix[rc[[1]][1], rc[[1]][2]]` bonus points.

* For the game `r row.names(rs1)[rc[[2]][1]]`, with a real score of `r paste(real[rc[[2]][1],], collapse = " - ")`, `r colnames(rs1)[rc[[2]][2]]` predicted `r paste(preds[[rc[[2]][2]]][rc[[2]][1],], collapse = " - ")` and won `r rs0[rc[[2]][1], rc[[2]][2]]` points and `r bonusMatrix[rc[[2]][1], rc[[2]][2]]` bonus points.

* For the game `r row.names(rs1)[rc[[3]][1]]`, with a real score of `r paste(real[rc[[3]][1],], collapse = " - ")`, `r colnames(rs1)[rc[[3]][2]]` predicted `r paste(preds[[rc[[3]][2]]][rc[[3]][1],], collapse = " - ")` and won `r rs0[rc[[3]][1], rc[[3]][2]]` points and `r bonusMatrix[rc[[3]][1], rc[[3]][2]]` bonus points as result was only correctly predicted by `r round(100 *  sum(rs0[rc[[3]][1],] > 0) / ncol(rs0))`%.

### Todo
* before first game, freeze the google sheet
* add real games results
* calculate scores of group stage
* construct table of next 8 games based on group stage results
* scoring system must adapts to:
    * prediction of final result only (after potential extra time and shootouts) ?
    * prediction of score at 90 minutes ?
