---
title: "Euro 2016 DIDE scores"
author: "Stephane"
date: "8 June 2016"
output: html_document
---

```{r}
library(knitr)
read_chunk('test.R')
```

```{r libs, warning=FALSE, message=FALSE}
```

Scoring system
```{r scoring system}

```

Load the google sheet
```{r read sheet}
```

Extract the predictions
```{r extract predictions}
```

Simulate real scores
```{r simulate real score}
```

Scoring function
```{r scoring function}
```

Results without bonus
```{r results without bonus}
```

Bonus
```{r bonus}
```


Final results
```{r final results}
```

```{r, results='asis'}
knitr::kable(rs1)
```

### Grand total
```{r grand total}
```


### Examples
```{r, echo = FALSE}
ex0 <- which(rs0 == 0, arr.ind = T) # zero
ex1 <- which(rs0 == 1 & bonusMatrix == 0, arr.ind = T) # 1 + no bonus
ex2 <- which(rs0 == 1 & bonusMatrix > 0, arr.ind = T) # 1 + bonus
ex3 <- which(rs0 == 3 & bonusMatrix == 0, arr.ind = T) # 3 + no bonus
ex4 <- which(rs0 == 3 & bonusMatrix > 0, arr.ind = T) # 3 + bonus

exs <- list(ex0, ex1, ex2, ex3, ex4)
rc <- list()
for (k in 1:length(exs)){
  rc[[k]] <- exs[[k]][sample(nrow(exs[[k]]), 1),]
}
v1 <- sapply(rc, function(x) row.names(rs1)[x[1]])
v2 <- sapply(rc, function(x) paste(real2[x[1],], collapse = " - "))
v3 <- sapply(rc, function(x) colnames(rs1)[x[2]])
v4 <- sapply(rc, function(x) paste(preds[[x[2]]][x[1],], collapse = " - "))
v5 <- sapply(rc, function(x) rs0[x[1], x[2]])
v6 <- sapply(rc, function(x) bonusMatrix[x[1], x[2]])
v7 <- sapply(rc, function(x) round(100 *  sum(rs0[x[1],] > 0) / ncol(rs0)))

text <- c()
for (i in 1:5){
text[i] <- paste("For the match ", v1[i], ", with a real score of ", v2[i],", ", v3[i], " predicted ", v4[i], " and won ", v5[i], " points and ", v6[i], " bonus points as result was correctly predicted by ", v7[i], "%", sep = "" )
}
```

* For the game `r v1[1]`, with a real score of `r v2[1]`, `r v3[1]` predicted `r v4[1]` and won `r v5[1]` points and `r v6[1]` bonus points.

* `r text[2]`

* `r text[3]`

* `r text[4]`

* `r text[5]`

### Todo
* before first game, freeze the google sheet
* add real games results
* calculate scores of group stage
* push results to a new sheet
* construct table of next 8 games based on group stage results
* scoring system must adapt to knockout stage:
    * prediction of final result only (after potential extra time and shootouts) ?
    * prediction of score at 90 minutes ?
